---
title: "Trachoma Report"
author: "Phong Le"
date: "9/22/2020"
output: html_document
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#knitr::opts_chunk$set(fig.width=6, fig.height=10) 

library(tidyverse)
library(kableExtra)
library(here)

# setwd("C:\\Users\\Phong\\Desktop\\Rollins Fall 2020\\INFO 550")
EU <- read.csv(here("EU.dummy.csv"))

```

```{r cleaning, echo=FALSE, warning=FALSE, message=FALSE}

#Cleaned one variable to remove excessive characters and limited data to real year ranges and no future projections
EU <- EU %>%
  rename(TT = TT_15plus)  %>%
  filter(survey_year <= 2020)

```

## Introduction

EU stands for evaluation unit. Each evaluation unit measures the incidence of Trachoma, and data has been collected from the years 2007 - 2020. There are two stages of Trachoma of interest (TF & TT). TF is the preliminary stage of Trachoma disease progression, and TI is an advanced stage. Among children, the mean TF prevalence is `r  round(mean(EU$TF),2)`%, and the mean TI prevalence is `r  round(mean(EU$TI),2)`%. TT is the final stage of Trachoma which involves serious scarring of the eye. This stage is mostly found in adults. Among adults, the mean prevalence of TT is `r  round(mean(EU$TT),2)`%. 

___

## Summary of Graphs/ Tables

Below you will find summarizing figures for the prevalence of Trachoma stages TF, TI, and TT over the course of 2007 - 2020. 

___

#### Summary TF, TI, and TT Prevalence Plot Over 2007-2020

```{r, plot1, echo = FALSE}

#Makes table arranging TF, TI, and TT by year
EU_Summary_Table <- EU %>%
  group_by(survey_year) %>%
  summarise(TF = round(mean(TF),2), TI = round(mean(TI),2), TT = round(mean(TT),2)) %>%
  rename("Survey Year" = survey_year) 

#Makes table arranging TF, TI, and TT by year
EU_Summary_Table %>%
  pivot_longer(!`Survey Year`, names_to = "Stage", values_to = "Prevalence") %>%
  ggplot(aes(`Survey Year`, Prevalence, color = Stage)) + 
  geom_point() +
  geom_line() +
  ggtitle("TF, TI, and TT Prevalence") +
  ylab("Prevalence") +
  theme(legend.position = "right")

```

___

#### Summary TF, TI, and TT Prevalence Table Over 2007-2020

```{r, table1, echo = FALSE}

#Makes table arranging TF, TI, and TT by year
EU_Summary_Table %>%
  kable() %>%
  kable_styling()

```

___

```{r}
getwd()
devtools::session_info()
```

___
